---
title: "R Notebook"
output: html_notebook
---

# Version info: R 3.2.3, Biobase 2.30.0, GEOquery 2.40.0, limma 3.26.8
# R scripts generated  Sun Nov 5 17:09:53 EST 2017


Server: www.ncbi.nlm.nih.gov
Query: acc=GSE37418&platform=GPL570&type=txt&groups=&colors=&selection=XXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXXX&padj=fdr&logtransform=auto&columns=ID&columns=adj.P.Val&columns=P.Value&columns=F&columns=Gene+symbol&columns=Gene+title&num=250&annot=ncbi

# SETUP
```{r}
#   Boxplot for selected GEO samples
library(Biobase)
library(GEOquery)

# load series and platform data from GEO
source("https://bioconductor.org/biocLite.R")

gset <- getGEO("GSE37418", GSEMatrix =TRUE, getGPL=FALSE)
if (length(gset) > 1) idx <- grep("GPL570", attr(gset, "names")) else idx <- 1
gset <- gset[[idx]]
expression_samples <- exprs(gset)
subgroups <- gset@phenoData@data$`subgroup:ch1`
expression_subgroup_samples <- rbind(expression_samples, subgroups)
subgroups <- expression_subgroup_samples[nrow(expression_subgroup_samples),]
```

# Dendrogram Clustering
# https://rpubs.com/gaston/dendrograms
```{r}
install.packages(ape)
dm = dist(t(expression_samples),method="euclidean")
hc = hclust(dm, method="single")
clus4 = cutree(hc, 4)
# G3, G4, WNT, SHH, UorSHH OUTLIER
mypal = c("#556270", "#4ECDC4", "#1B676B", "#FF6B6B", "#C44D58")
op = par(bg = "#E8DDCB")
# plot.phylo(as.phylo(hc), type= "fan", tip.color = mypal[clus4], label.offset = 1, cex = 0.5, col = "red",no.margin = TRUE)
plot.phylo(as.phylo(hc), type= "fan",  label.offset = 1, cex = 0.5, col = "red",no.margin = TRUE)
```

# TODO
```{r}
# function to get color labels
colLab <- function(n) {
  if (is.leaf(n)) {
    a <- attributes(n)
    labCol <- labelColors[clusMember[which(names(clusMember) == a$label)]]
    attr(n, "nodePar") <- c(a$nodePar, lab.col = labCol)
  }
  n
}

# using dendrapply
clusDendro = dendrapply(hcd, colLab)

# make plot
plot(clusDendro, main = "Cool Dendrogram", type = "triangle")
```





# KMeans Clustering
kmeans(t(ex), 4)
clustering <- kmeans(t(ex), 4)

# KMeans Graphing Clusters
# TODO kmeans
# https://datascienceplus.com/k-means-clustering-in-r/
library(ggplot2)
# TODO hier
# https://www.r-bloggers.com/hierarchical-clustering-in-r-2/



# PCA
sj.pca <- prcomp(t(ex)) 
plot(predict(sj.pca))


# set parameters and draw the plot

<!-- dev.new(width=4+dim(gset)[[2]]/5, height=6) -->
<!-- par(mar=c(2+round(max(nchar(sampleNames(gset)))/2),4,2,1)) -->
<!-- title <- paste ("GSE37418", '/', annotation(gset), " selected samples", sep ='') -->
<!-- boxplot(exprs(gset), boxwex=0.7, notch=T, main=title, outline=FALSE, las=2) -->



